Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-04-04 PAPER.tex
changed P_out's to have hats (estimates) and some of the P_in's as well

We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as

\begin{equation}
\label{eq:Pin}
P_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
P_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a non-diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.

The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data. Therefore, $P_{\rm out}$ can be directly compared to the measurement that we make.

@@

%\begin{equation}
%P_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
%\end{equation}
%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}

Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:

@@

%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$. We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).

@@

%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline. \dcj{Here is the post-hoc justification for this signal loss method.  Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum. So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}. Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example. The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation. Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}

@@

%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
%which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 

@@

%\subsubsection{Signal Loss Illustration}
%\label{sec:Illustration}
%To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:

\begin{eqnarray}
\label{eq:crossterm_full}
P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:

\begin{eqnarray}
\label{eq:crossterm}
P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$). We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are Gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{P_e}\sqrt{P_x}$. We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected. %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e. in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).  However, it is useful as a check of our system in a relatively simple case. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green). Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the estimated inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{P_e}\sqrt{P_x}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
in this regime the cross-term has nearly the same amplitude, but with a negative sign. As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.  This negative component drives down the $P_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.

%A brief description of Figure \ref{fig:sigloss_terms} is as follows. The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed. The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$). It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$. The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$. This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray). It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case. We see that the cross-terms can produce a large, negative signal which serves to reduce $P_{\rm out}$ and drive the bulk of our loss. In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $P_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).

%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}. For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$. It is in this limit where we expect signal loss to be greatest, and $P_{\rm out}$ becomes:
%
%\begin{eqnarray}
%\label{eq:pout_expand}
%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
%\end{eqnarray}
%The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone. Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss. However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss. In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$. Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
data. Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}. The output power spectrum ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation 
\eqref{eq:crossterm} are shown in blue, red, and green. The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss). The details of the simulation used to generate the figure is explained in Section 
\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
term with width $\sqrt{P_e}\sqrt{P_x}$. However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

>>>>

We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as

\begin{equation}
\label{eq:Pin}
\widehat{P}_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
\widehat{P}_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a non-diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.

The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute the true $\widehat{P}_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data. Therefore, $\widehat{P}_{\rm out}$ can be directly compared to the measurement that we make.

@@

%\begin{equation}
%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
%\end{equation}
%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}

Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:

@@

%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$. We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).

@@

%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline. \dcj{Here is the post-hoc justification for this signal loss method.  Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum. So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}. Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example. The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation. Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}

@@

%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 

@@

%\subsubsection{Signal Loss Illustration}
%\label{sec:Illustration}
%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:

\begin{eqnarray}
\label{eq:crossterm_full}
\widehat{P}_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:

\begin{eqnarray}
\label{eq:crossterm}
\widehat{P}_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$). We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are Gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$. We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected. %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e. in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).  However, it is useful as a check of our system in a relatively simple case. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green). Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the estimated inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
in this regime the cross-term has nearly the same amplitude, but with a negative sign. As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.  This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.

%A brief description of Figure \ref{fig:sigloss_terms} is as follows. The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed. The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$). It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$. The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$. This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray). It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case. We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss. In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).

%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}. For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$. It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
%
%\begin{eqnarray}
%\label{eq:pout_expand}
%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
%\end{eqnarray}
%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone. Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss. However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss. In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$. Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
data. Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}. The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation 
\eqref{eq:crossterm} are shown in blue, red, and green. The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss). The details of the simulation used to generate the figure is explained in Section 
\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$. However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
